$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-05 paper/paper.tex
Small fixes

\begin{note}
  \label{note:linearity}
  We will often work with pairs of input and output multiplicities.
  We use the notation $\type{C}^{\func{2}}$ to stand for a $\type{C} \times \type{C}$ tuple of input and output multiplicities, respectively.
  We use $\opsquared{x}{y}{z}$ to stand for a monoidal operation on pairs of multiplicities -- where the algebraic laws are lifted element-wise.

@@

    \item [Shared]
    The carrier is a type with a single trivial constructor $\constr{\omega}$.
    Both $\zero$ and $\one$ are instantiated to $\constr{\omega}$.
    The relation $\op{\constr{\omega}}{\constr{\omega}}{\constr{\omega}}$ is inhabited.
    All the properties of the algebra follow trivially.
    All shared channels have multiplicities $(\omega \comma \omega)$, which they will forever preserve.
\end{description}

>>>>

\begin{note}
  \label{note:linearity}
  We will often work with pairs of input and output multiplicities.
  We use the notation $\type{C}^{\func{2}}$ to stand for a $\type{C} \constr{\times} \type{C}$ tuple of input and output multiplicities, respectively.
  We use $\opsquared{x}{y}{z}$ to stand for a monoidal operation on pairs of multiplicities -- where the algebraic laws are lifted element-wise.

@@

    \item [Shared]
    The carrier is a type with a single trivial constructor $\constr{\omega}$.
    Both $\zero$ and $\one$ are instantiated to $\constr{\omega}$.
    The relation $\op{\constr{\omega}}{\constr{\omega}}{\constr{\omega}}$ is inhabited.
    All the properties of the algebra follow trivially.
    Shared channels have multiplicities $(\constr{\omega} \comma \constr{\omega})$, which they will forever preserve.
\end{description}
